\pagenumbering{arabic}
\chapter{Introduction}
\section{Overview}
The aim of the “Transcoding Website Usability Survey” is to gather feedback from users about the usability of a transcoding website, to identify areas for improvement and make necessary changes that will enhance the user experience.

\section{How Long Will the Survey Take?}
Due to the comprehensive nature of the survey and the depth of feedback that is being sought, it is expected that the survey may take up to two hours to complete. This estimate is based on the average amount of time it takes for users to provide thoughtful and detailed responses to the survey questions. It also accounts for the downloading of the source files for the survey, as well as upload, transcode, and download times.

\section{This Document}
This document has been created so that you have the option to record your answers, pause the survey, and return later if you need to. We encourage participants to complete the survey in one sitting. 

\clearpage

\section{How Your Data Is Stored and Used}
All responses to the “Transcoding Website Usability Survey” are treated with strict confidentiality and anonymity. This means that no personally identifiable information will be collected from respondents, and no identifying details will be associated with any feedback provided. The use of anonymity in this survey ensures that respondents are able to provide candid and truthful feedback without any fear of retribution or social desirability bias. By upholding ethical principles of anonymity, the survey is able to collect accurate and reliable data, leading to more informed decision-making and improved user experience for the transcoding website.

\section{Participant Information and Consent}
Please ensure you read the Participant Information and Consent Form.
\\
You can access it at:
\\
\href{https://1drv.ms/u/s!AhkIcseg6EOIiqYVk9AZDHGkKqjyCQ?e=tt5A6d}{\url{https://1drv.ms/u/s!AhkIcseg6EOIiqYVk9AZDHGkKqjyCQ?e=tt5A6d}}
\newline
\textbf{Please retain a copy of this document.}

\section{What You Need to Participate}

\begin{itemize}
\item 1 hour
\item A laptop or desktop computer
\item 2 GB of free space on your device
\item Permission to install applications on your device for one of the services
\item An Internet connection
\item The \emph{Big Buck Bunny} video in \emph{Standard 2D, 1080p, 60FPS}
\end{itemize}

\emph{During this survey, you will be required to upload and download video files. These video files will be provided to you, and you must only use the provided videos for the purpose of this survey.
You can download Big Buck Bunny directly from \href{http://distribution.bbb3d.renderfarming.net/video/mp4/bbb_sunflower_1080p_60fps_normal.mp4}{this link} (\href{http://distribution.bbb3d.renderfarming.net/video/mp4/bbb_sunflower_1080p_60fps_normal.mp4}{\url{http://distribution.bbb3d.renderfarming.net/video/mp4/bbb_sunflower_1080p_60fps_normal.mp4}}). If a video player is displayed, it should provide an option to download the file within the menu accessed by clicking on the \textbf{$\vdots$} icon in the bottom right of the player.}

\section{How Do I Submit My Responses?}
You can submit your responses anonymously in this \href{https://forms.office.com/e/nGatwzvGUq}{Microsoft Forms form}:\newline
\centerline{ \href{https://forms.office.com/e/nGatwzvGUq}{\url{https://forms.office.com/e/nGatwzvGUq}}} \newline
You can submit this document, or a document of just your answers, via email. Please send your answers and a signed consent form to: \newline
\centerline{\href{mailto://1900040@abertay.ac.uk}{1900040@abertay.ac.uk}}\newline
You can submit this document in person alongside a signed consent form by contacting Ben Fleuty.

\section{What If I Wish to Not Answer a Question?}
You are free to answer or skip any and all questions. If you wish to skip a question, simply record that in a way that makes sense to you when undertaking the survey. When you are submitting your responses in the form, select the option stating that you wish to opt out of this question or leave it blank, whichever if appropriate.